
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Appendix
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{CONCEPTS, AND DEFINITIONS}
This appendix provides a list of acronyms and abbreviations used throughout this dissertation, as well as simplified definitions of the most important concepts needed to understand the contents of
this dissertation.
\section{Acronyms and Abbreviations}
This section provides a list the acronyms and abbreviations used in this dissertation,
listed alphabetically.
\begin{itemize}

\item OFDM: Orthogonal Frequency Division Multiplexing

\item TDD: Time Division Duplex.

\end{itemize}

\section{Concepts and Terminology}
This section provides definitions of the most important concepts and terminology
needed to understand this dissertation, listed alphabetically by term, acronym,
or abbreviation.

\begin{itemize}
\item Destination node: The radio node that receives data packets over the air from the source node and send the received packets to the server.

\item Disable muter: Forward data samples from the USRP to next signal processing block.

\item Enable muter: Block the data samples from the USRP.

\item Forward link: Transmission from the source node to the destination.

\item Muter: A GNU radio block in the receiver that blocks the data from the USRP when current node is in the transmission state of a TDD cycle and that let the data from the USRP go through to next signal processing block when current node is in receiving state.

\item Packet: Data of 1400 bytes.

\item Physical-layer packet: packet that physical layer transmits in each subband.

\item Reverse link: Transmission from the destination node to the source.

\item Server: The server that sends data packet to the source node when requested by the source node and that receives and verifies the data packets sent from the destination node.

\item Source node: The radio node that requests data packets from the server and try to transmit them over the air.

\item Sub-packet: Packet that are pieces of the Packet in order to fit the physical-layer packet size requirement of the physical layer.

\item Tagger: A block that lies between the transmitter flow graph and the USRP in TDD mode, and that controls the burst transmission time in TDD mode.

\item TDD frame: The transmission period of a TDD cycle.

\item TDD sub-frame: A collection of Physical-layer packets that is synchronized by one group of preamble. Each sub-frame contains multiple physical-layer packets across the 5MHz frequency and during one TDD sub-frame, each OFDM tone only serves one Physical-layer packet.

\item Sub-frame left: a variable indicating how many sub frames are left in current TDD frame. Sub-frame left is contained in very physical-layer packet with one byte.
\end{itemize}
